A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and coral bleaching as an alternate stable state

### 2017-03-22 JTB_ms/JTB_ms.tex
remake after fix ss oscill filter

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Alternate stable states in S:H biomass and growth across a
light gradient. Alternate stable states occur between
\textasciitilde{}25-42 mol photons m\textsuperscript{-2}
d\textsuperscript{-1} under these conditions (DIN=1e-7 molN
L\textsuperscript{-1}; X=1e-7 CmolX L\textsuperscript{-1}), depending on
whether initial S:H is high (1, closed circles), representing a healthy
coral, or low (0.0001, open circles), representing a bleached coral.
Arrow above point at L=25 indicates a S:H ratio beyond the axis range;
this `overshoot' phenomenon, in which initially bleached corals may
achieve high S:H ratios while remaining in a carbon-limited state is
discussed in the \emph{Coral Bleaching and Recovery} section.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Alternate stable states in S:H biomass and growth across a
light gradient. Alternate stable states occur between
\textasciitilde{}25-42 mol photons m\textsuperscript{-2}
d\textsuperscript{-1} under these conditions (DIN=1e-7 mol N
L\textsuperscript{-1}; X=1e-7 C-mol X L\textsuperscript{-1}), depending
on whether initial S:H is high (1, closed circles), representing a
healthy coral, or low (0.0001, open circles), representing a bleached
coral. Arrow above point at L=25 indicates a S:H ratio beyond the axis
range; this `overshoot' phenomenon, in which initially bleached corals
may achieve high S:H ratios while remaining in a carbon-limited state is
discussed in the \emph{Coral Bleaching and Recovery} section.}
\end{figure}
